\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}
(Type your content here.)

# outils utils pour la recherche

ResearchRabbit
Zotero
Google Scholar
LaTeX
Overleaf

https://github.com/yuchenlin/rebiber
https://github.com/google-research/arxiv-latex-cleaner 
https://capitalizemytitle.com/
https://flamingtempura.github.io/bibtex-tidy/index.html 

# outils pour le développement
Deep learning frameworks : TensorFlow, PyTorch, Tax, Keras
Machine learning important tools : Numpy, Pandas, Matplotlib/Seaborn/Plotly
Experiment tracking : Wandb, MLflow
Google Colab/Jupyter Notebook, Kaggle
Hyperparameter tuning : Optuna, Ray Tune, Hyperopt

# LLMs 

Je recommande d’utiliser un LLM UNIQUEMENT SI vous pouvez vérifier l’output. 

LLMs disponibles : 

ChatGPT (toujours désactivé l’entraînement sur les données)
Claude (selon leurs conditions d’utilisation, ils n’utilisent pas les données par défaut. Toutefois, ils ont quand même utilisés les donnés dans le papier de Clio (https://www.anthropic.com/research/clio) )
Le chat (Mistral) (ils disent que les données ne sont pas utilisées : https://help.mistral.ai/en/articles/156194-does-mistral-ai-exploit-users-data-to-train-its-models et que whatever données qui doivent être supprimées peuvent être fait en leur écrivant : https://help.mistral.ai/en/articles/154193-how-can-i-exercise-my-gdpr-rights) 
Meta.ai (il ne semble pas y avoir d’options)
DeepSeek (selon ce post, c’est vraiment pas une bonne idée : https://medium.com/data-science-in-your-pocket/dont-use-deepseek-v3-895be7b853b0. 
According to DeepSeek’s terms, you are fully responsible for all Inputs submitted to their services and the corresponding Outputs. This means:
You must ensure you have the legal rights, licenses, and permissions to submit any data.
You alone are liable if your Inputs or Outputs breach any laws or regulations.
Data Privacy Concerns: Even minimal usage of your data creates potential risks of misuse or leaks.
No Clear Opt-Out: Unless you give explicit separate consent, they may still use your data for service-related purposes.
You cannot use, copy, or even display any content or software from DeepSeek without permission.
Any misuse, even unintentional, may lead to legal action from DeepSeek.

 
Gemini (might not be able to opt out of data being used to train the model : https://www.googlecloudcommunity.com/gc/AI-ML/Use-of-your-data-for-product-improvement-purposes-in-the-Google/m-p/723832) 
Copilot (payé par l’université pour garantir la non-utilisation des données)

\end{document}